---
title: "Quantmod: Vanguard ETF Funds"
format: html
editor: visual
---

```{r}
#| echo: false
#| message: false
#| warning: false

library(quantmod)
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
```

```{r}
rm(list=ls())
ETF = c("BND","BNDX","VTI","VXUS")
getSymbols(ETF, from='2024-04-29')
summary(BND)
```

# Basic Stock Plots

```{r}
chartSeries(BND,type="line", TA = 'addBBands(n = 20, sd = 2, maType = "SMA", draw = "bands", on = -1)',theme="white")

```

```{r}
chartSeries(BND,type='line',
            subset = "last 4 months",
            theme="white",
            TA = NULL)
addSMA(n=50)
title(main="BND Daily Close")
            
```

```{r}
chartSeries(BND,
            type="line", 
            subset = "last 4 months",
            theme="white",
            TA = "addSMA(n=50)")
```

## Plot "types": 

* "auto" =>	Automatically chooses a chart type (default)
* "candlesticks" =>	Classic candlestick chart with OHLC data
* "matchsticks" =>	Similar to candlesticks, but thinner lines
* "bars" =>	OHLC bar chart
* "line" =>	Line chart using closing prices (or selected data)
* "histogram" =>	Typically used for volume or other indicators
* "ohlc"  => 	Like bars, another OHLC representation

```{r}
chartSeries(BND,
            type="bars", 
            subset = "last 4 months",
            theme="white",
            TA = "addMACD()")
```

```{r}
chartSeries(BND,
            type="candlestick", 
            subset = "last 4 months",
            theme="white",
            TA = "addRSI()"
            )
```
```{r}
chartSeries(BND,
            type="matchsticks", 
            subset = "last 4 months",
            theme="white",
            TA = "addMACD()")
```

# Dividends Since 2020

```{r}
divs <- getDividends("BND", from = "2022-01-01")
plot(divs, main = "BNDX Dividend History", ylab = "Dividend ($)", col = "darkgreen", type = "h")
hist(divs)
```

# Returns Daily, Weekly and Monthly

```{r}
dr <- dailyReturn(BND)
plot(dr)
boxplot(dr)
hist(dr)
```
```{r}
wr <- weeklyReturn(BND)
plot(wr)
boxplot(wr)
hist(wr)
```

```{r}
mr <- monthlyReturn(BND)
plot(mr)
boxplot(mr)
hist(mr)
```

