---
title: "Quantmod: Vanguard ETF Funds"
format: html
editor: visual
---

```{r}
#| echo: false
#| message: false
#| warning: false

library(quantmod)
library(alphavantager)
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
```

```{r}
rm(list=ls())

source("./alpha_vantage.R")
ETF = c("BND","BNDX","VTI","VXUS")
getSymbols("BND", src = "av", api.key = av_api_key)
```

# Basic Stock Plots

```{r}
chartSeries(BND,
            subset="last 30 days",
            TA= NULL,
            name="Vandgauar BND ETF(last 30 days")
addSMA(n=20)
```



```{r}
chartSeries(BND,type='line',
            subset = "last 4 months",
            theme="white",
            TA = NULL)
addSMA(n=20)

            
```

```{r}
chartSeries(BND,
            type="line", 
            subset = "last 4 months",
            theme="white",
            TA = "addSMA(n=20)")
```
```{r}
# chartSeries(BND,type="line", TA = 'addBBands(n = 20, sd = 2, maType = "SMA", draw = "bands", on = -1)',theme="white")
chartSeries(BND,
            type="line", 
            TA = 'addBBands()',
            theme="white",
            subset="last 60 days")
```

## Plot "types":

-   "auto" =\> Automatically chooses a chart type (default)
-   "candlesticks" =\> Classic candlestick chart with OHLC data
-   "matchsticks" =\> Similar to candlesticks, but thinner lines
-   "bars" =\> OHLC bar chart
-   "line" =\> Line chart using closing prices (or selected data)
-   "histogram" =\> Typically used for volume or other indicators
-   "ohlc" =\> Like bars, another OHLC representation

```{r}
chartSeries(BND,
            type="bars", 
            subset = "last 4 months",
            theme="white",
            TA = "addMACD()")
```

```{r}
chartSeries(BND,
            type="candlestick", 
            subset = "last 4 months",
            theme="white",
            TA = "addRSI()"
            )
```

```{r}
chartSeries(BND,
            type="matchsticks", 
            subset = "last 4 months",
            theme="white",
            TA = "addMACD()")
```

# Dividends Since 2020

```{r}
divs <- getDividends("BND", from = "2022-01-01")
plot(divs, main = "BNDX Dividend History", ylab = "Dividend ($)", col = "darkgreen", type = "h")
hist(divs)
```

# Returns Daily, Weekly and Monthly

```{r}
dr <- dailyReturn(BND)
plot(dr)
boxplot(dr)
hist(dr)
```

```{r}
wr <- weeklyReturn(BND)
plot(wr)
boxplot(wr)
hist(wr)
```

```{r}
mr <- monthlyReturn(BND)
plot(mr)
boxplot(mr)
hist(mr)
```
